A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-15 doc/sigchi14/control.tex
update Likert Ratings: Home Control Scenario

\subsection{Methodology}
We recreated a living room environment that had four controllable appliances: a fan, a lamp, and two laptops functioning as an audio and video player, respectively (see Figure~\ref{fig:smarthome}). The fan and lamp had binary controls: they could be switched on or off. The laptops had multiple parameterized functions: participants could start, pause, stop, and rewind  video and audio, and adjust volume.

We then asked users to work through the following script for controlling the room for watching a movie in the evening:
{\small
\begin{enumerate}
\item Turn off the lights as you want to watch the movie in a darkened room.
\item You feel a little hot in the room, so you turn on the fan.
\item You connect to the Smart TV and start playing the movie. 
\item The volume seems too soft to hear over the fan- turn it up a bit. 
\item After a while, you want to take a break to get a snack. Pause the movie. 
\item When you come back, you've forgotten what was said last - rewind by ~30 seconds and restart the movie. 
\item When the credits roll, you stop the movie and turn the lights back on.
\item You want to listen to some music.
\item After awhile, you stop the music you turn off the fan and leave the room.
\end{enumerate}
}

>>>>

\subsection{Methodology}
We recreated a living room environment that had three controllable appliances: a fan, a lamp, and one laptop functioning as a video player, respectively (see Figure~\ref{fig:smarthome}). The fan and lamp had binary controls: they could be switched on or off. The laptop had multiple parameterized functions: participants could start, pause, fastforward, rewind, and adjust volume.

We then asked users to work through the following script for controlling the room for watching a movie in the evening:
{\small
\begin{enumerate}
\item Turn off the lights as you want to watch the movie in a darkened room.
\item You feel a little hot in the room, so you turn on the fan.
\item You connect to the Smart TV and start playing the movie. 
\item The volume seems too soft to hear over the fan- turn it up a bit. 
\item After a while, you want to take a break to get a snack. Pause the movie. 
\item When you come back, you've forgotten what was said last - rewind by ~30 seconds and restart the movie. 
\item When the credits roll, you stop the movie and turn the lights back on.
\item After awhile, you turn off the fan and leave the room.
\end{enumerate}
}
